Structured Nonlinear Feedback Design with Separable Control-Contraction Metrics

### 2016-10-28 R0V0.tex
Edit section about distributed synthesis

Consider the graph $\mathscr{G}=(\mathscr{V},\mathscr{E})$ describing the topology of the network~\eqref{eq:general system}. A \emph{clique} $\mathscr{C}\subset\mathscr{V}$ of the graph $\mathscr{G}$ is the maximal set of nodes that induces a complete subgraph on $\mathscr{G}$. A \emph{chord} of a path is any edge joining two nonconsecutive nodes. A graph is said to be \emph{chordal} if every cycle greater than three has a chord. The importance of a graph being chordal is that it has a tree-decomposition into cliques  \cite[Proposition~12.3.11]{Diestel2005}.

\begin{proposition}\label{prop:}
	Let $p\in\mathbb{N}_{>0}$ be the number of cliques of the graph $\mathscr{G}$. Then, the MI~\eqref{eq:MI formulation} can be decomposed into $p$ matrix inequalities with smaller dimension.
\end{proposition}

\begin{proof}
	The number of cliques $p$ in the $\mathscr{G}$ can be computed using the algorithm \cite{BronKerbosch1973}. The remainder of this proof is based on Section~II of \cite{PakazadHanssonAndersenEtAl2015}.

>>>>

Consider the graph $\mathscr{G}=(\mathscr{V},\mathscr{E})$ describing the topology of the network~\eqref{eq:general system}. A \emph{clique} $\mathscr{C}\subset\mathscr{V}$ of the graph $\mathscr{G}$ is the maximal set of nodes that induces a complete subgraph on $\mathscr{G}$. A \emph{chord} of a path is any edge joining two nonconsecutive nodes. A graph is said to be \emph{chordal} if every cycle greater than three has a chord. The importance of a graph being chordal is that it has a tree-decomposition into cliques  \cite[Proposition~12.3.11]{Diestel2005} such a tree is said to a \emph{clique tree} and it is denote as $\mathscr{T}(\mathscr{G})$.

\begin{proposition}\label{prop:}
	Let $p\in\mathbb{N}_{>0}$ be the number of nodes of the clique tree $\mathscr{T}(\mathscr{G})$. Then, the MI~\eqref{eq:MI formulation} can be decomposed into $p$ matrix inequalities with smaller dimension.
\end{proposition}

\begin{proof}
\todo[inline]{Continue with the proof}

	The number of cliques $p$ in the $\mathscr{G}$ can be computed using the algorithm \cite{BronKerbosch1973}. The remainder of this proof is based on Section~II of \cite{PakazadHanssonAndersenEtAl2015}.
